Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
killed a fixed figure and made it smaller to free up space again
began ahrs

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

@@

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_isometric.png}}
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_side.png}}
\\
	\subfloat[Photograph of pan tilt unit installed in \emph{Daedalus}]{\label{fig:pantilt_photo}
			\includegraphics[width=0.75\textwidth]{../images/pantilt_photo1.jpg}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkplots} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

\begin{figure} [H]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationControls.jpg}
  	\caption[Image Station Control Panel]{The Control Panel for the Image Station.  Above is a live video feed from the plane.  Below are controls to adjust the pan/tilt of the unit, zoom in/out, take a picture, and reset the camera to a neutral position.}
  	\label{fig:imagestationcontrols}
\end{figure}

>>>>

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.5\textwidth}
	\includegraphics[width=0.47\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

@@

Early in the school year, we built a thermopile-based attitude (pitch and roll) sensor very similar to the sensor design used by the Paparazzi Tiny autopilot. Accompanied by a driver which allowed it to appear to the airborne software just as it would on the Tiny, this simple analog sensor helped us prototype and test the Paparazzi system. Having built a superior sensor, we keep it as a backup. It is detailed in Figure \ref{fig:hardware_conn_diagram} although we do not intend to use it for the competition.

Thanks to sensor donations from Invensense and ST Micro, we were able to build a 9 axis Attitude and Heading Reference Sensor (AHRS) from an Invensense ITG-3200 3-axis rate gyro \cite{itg3200} and an ST Micro LSM303DLH 3-axis accelerometer and magnetometer. \cite{lsm303dlh}

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_isometric.png}}
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_side.png}}
\\
	\subfloat[Photograph of pan tilt unit installed in \emph{Daedalus}]{\label{fig:pantilt_photo}
			\includegraphics[width=0.55\textwidth]{../images/pantilt_photo1.jpg}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkplots} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

\begin{figure}
  \centering
  	\includegraphics[width=0.5\textwidth]{../images/ImageStationControls.jpg}
  	\caption[Image Station Control Panel]{The Control Panel for the Image Station.  Above is a live video feed from the plane.  Below are controls to adjust the pan/tilt of the unit, zoom in/out, take a picture, and reset the camera to a neutral position.}
  	\label{fig:imagestationcontrols}
\end{figure}
